%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
    {DevOps Engineer} % Job title
    {KarrotPay Inc. (Intern)} % Organization
    {Seoul, S.Korea} % Location
    {Jun. 2023 - Oct. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked as a DevOps Engineer at KarrotPay Inc. in 2023 Karrot Summer Tech Internship.}
        \item {Developed DevOps tools to improve developer productivity in KarrotPay.}
        \item {Performed other DevOps/SRE tasks.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Backend Engineer \& DevOps Engineer} % Job title
    {NAVER Corp. (Contract)} % Organization
    {Seoul, S.Korea} % Location
    {Feb. 2023 - Jun. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed Sharded Cluster Mode for Yorkie, a open source document store for building collaborative editing applications.}
        \item {Built Yorkie Sharded Cluster Mode on Kubernetes with Istio, and packaged with Helm Chart.}
        \item {Rebuilt Yorkie SaaS devops system with Terraform, ArgoCD, Prometheus, Grafana, and Loki.}
        \item {Implemented several features and optimization in Yorkie server.}
        \item {Implemented yorkie.tree CRDT structure in Go SDK.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {2023 Open Frontier Developer \& Mentor} % Job title
    {Open Frontier (National IT Industry Promotion Agency)} % Organization
    {Seoul, S.Korea} % Location
    {Mar. 2023 - Nov. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Participated in 2023 Open Frontier as a developer of Yorkie project.}
        \item {Participated in 2023 Opensource Playground as a mentor of Yorkie project.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Dev Leader \& Backend Engineer} % Job title
    {S/W Maestro (Institute of ICT Planning \& Evaluation)} % Organization
    {Seoul, S.Korea} % Location
    {Mar. 2022 - Nov. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Planned and developed Asyncrum, a remote collaborate tool with real-time collaboration whiteboard and daily video logs.}
        \item {Developed overall software delevoping process and architecture for Asyncrum.}
        \item {Designed entire backend architecture and built AWS infrastructure.}
        \item {Built Asyncrum backend CI/CD pipeline with Jenkins and ArgoCD.}
        \item {Prototyped and implemented real-time collaboration whiteboard with tldraw and Yorkie.}        
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {PH2Y (Sejong University)} % Organization
    {Seoul, S.Korea} % Location
    {Jul. 2021 - Jun. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Planned and developed Bulter's Note, a map based pet related information platform service on Android.}
        \item {Optmized backend image processing service with imgscalr, a Java image scaling-library.}
        \item {Implemented video streaming service using HTTP range request.}
      \end{cvitems}
    }

%---------------------------------------------------------
  % \cventry
  %   {Software Engineer} % Job title
  %   {ShitOne Corp.} % Organization
  %   {Seoul, S.Korea} % Location
  %   {Dec. 2011 - Feb. 2012} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Developed a proxy drive smartphone application which connects proxy driver and customer.}
  %       \item {Implemented overall Android application logic and wrote API server for community service, along with lead engineer who designed bidding protocol on raw socket and implemented API server for bidding.}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------
\end{cventries}
