%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Maintainer} % Affiliation/role
    {Yorkie} % Organization/group
    {Yorkie Team} % Location
    {Mar. 2023 - } % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Yorkie is an open source document store for building collaborative editing applications.}
        \item {Maintainer, developer, and mentor for the Yorkie project.}
        \item {Designed and developed the Yorkie Sharded Cluster Mode.}
        \item {Built Yorkie SaaS infrastructure environment.}
        \item {Improved RPC protocol of Yorkie server and client.}
        \item {Improved and stabilized the performance of the Yorkie server.}
        \item {Developed a Yorkie real-time collaborative whiteboard example.}
        \item {Suggested features, optimizations, issues, etc. for the Yorkie project as a whole.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
  {Member} % Affiliation/role
  {Kubernetes} % Organization/group
  {kubernetes-sig-docs} % Location
  {Apr. 2023 - } % Date(s)
  {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {Kubernetes is an open source system for managing containerized applications across multiple hosts.}
      \item {Participated in kubernetes-sig-docs project as a Korean localization team member.}
      \item {Translated and updated various documents related to Kubernetes in Korean.}      
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
    {Member} % Affiliation/role
    {Istio} % Organization/group
    {Istio Community} % Location
    {Apr. 2023 - } % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Istio is an open source service mesh that layers transparently onto existing distributed applications.}
        \item {Participated in Istio project as a community member.}
        \item {Udated documentation related to gRPC probe health checking.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Open Frontier Developer \& Mentor} % Affiliation/role
    {Open Frontier (National IT Industry Promotion Agency)} % Organization/group
    {Seoul, S.Korea} % Location
    {Mar. 2023 - Nov. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Participated in 2023 Open Frontier as a developer of Yorkie project.}
        \item {Participated in 2023 Opensource Playground as a mentor of Yorkie project.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Affiliation/role
    {S/W Maestro (Institute of ICT Planning \& Evaluation)} % Organization/group
    {Seoul, S.Korea} % Location
    {Mar. 2022 - Nov. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Planned and developed Asyncrum, a remote collaborate tool with real-time collaboration whiteboard and daily video logs.}
        \item {Developed overall software delevoping process and architecture for Asyncrum.}
        \item {Designed entire backend architecture and built AWS infrastructure.}
        \item {Built Asyncrum backend CI/CD pipeline with Jenkins and ArgoCD.}
        \item {Prototyped and implemented real-time collaboration whiteboard with tldraw and Yorkie.}        
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Affiliation/role
    {PH2Y (Sejong University)} % Organization/group
    {Seoul, S.Korea} % Location
    {Jul. 2021 - Jun. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Planned and developed Bulter's Note, a map based pet related information platform service on Android.}
        \item {Optmized backend image processing service with imgscalr, a Java image scaling-library.}
        \item {Implemented video streaming service using HTTP range request.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
